---
title: "CE Income Item Non-response or Invalid Response:  Towards a Predictive Model"
author: "Mark Frame"
date: "December 2, 2018"
output: html_notebook
---

```{r setup, include=FALSE}
install.packages("knitr")
knitr::opts_chunk$set(echo = TRUE)
```
s

```{r}
install.packages("tidyverse")
install.packages("GGally")
install.packages("mlbench")
install.packages("boot")
install.packages("glmnet")
install.packages("caret")
install.packages("gglasso")
install.packages("RSocrata")
install.packages("ggplot2")
install.packages("ggmap")
install.packages("e1071")
install.packages("class")
install.packages("PRROC")
install.packages("pROC")
install.packages("titanic")
install.packages("rpart")
```

```{r}
install.packages("party")
install.packages("partykit")
install.packages("verification")
install.packages("strucchange")
install.packages("foreach")
install.packages("pdp")
```

```{r}
install.packages("plotmo")
install.packages("randomForest")
install.packages("fastAdaboost")
install.packages("gbm")
install.packages("xgboost")
install.packages("mboost")
install.packages("ranger")
install.packages("devtools")
```

```{r}
devtools::install_github("AppliedDataSciencePartners/xgboostExplainer")
```

```{r}
install.packages("spam")
```

```{r}
install.packages("fields")
```

```{r}
install.packages("verification")
```

```{r}
install.packages("missForest")
```

```{r}
install.packages("caret")
```

```{r}
install.packages("caretEnsemble")
install.packages("SuperLearner")
install.packages("subsemble")
install.packages("smotefamily")
install.packages("DMwR")
```

```{r}
install.packages("gbm")
install.packages("e1071")
```

```{r}
library(tidyverse)
library(GGally)
library(mlbench)
library(boot)
library(glmnet)
library(caret)
library(gglasso)
library(RSocrata)
library(ggplot2)
library(ggmap)
library(e1071)
library(class)
library(PRROC)
library(pROC)
library(titanic)
library(rpart)
library(party)
library(partykit)

library(strucchange)
library(foreach)
library(pdp)
library(plotmo)
library(randomForest)
library(fastAdaboost)
library(gbm)
library(xgboost)
library(mboost)
library(ranger)
library(devtools)
```

```{r}
library(missForest)
```

```{r}
library(verification)
```

```{r}
library(caretEnsemble)
library(SuperLearner)
library(subsemble)
library(smotefamily)
library(DMwR)
```

```{r}
library(xgboostExplainer)
```

```{r}
search()
```


```{r}
MEMD_1=read.csv("D:/memd141.csv", header = TRUE, sep=',')
MEMD_2=read.csv("D:/memd142.csv", header = TRUE, sep=',')
MEMD_3=read.csv("D:/memd143.csv", header = TRUE, sep=',')
MEMD_4=read.csv("D:/memd144.csv", header = TRUE, sep=',')

```

```{r}
MEMD_FMLD_141_1=read.csv("D:/memd_fmld141_1_1118",header=TRUE,sep=',')
MEMD_FMLD_142_1=read.csv("D:/memd_fmld142_1_1118",header=TRUE,sep=',')
MEMD_FMLD_143_1=read.csv("D:/memd_fmld143_1_1118",header=TRUE,sep=',')
MEMD_FMLD_144_1=read.csv("D:/memd_fmld144_1_1118",header=TRUE,sep=',')
MEMD_FMLD_151_1=read.csv("D:/memd_fmld151_1_1118",header=TRUE,sep=',')
MEMD_FMLD_152_1=read.csv("D:/memd_fmld152_1_1118",header=TRUE,sep=',')
MEMD_FMLD_153_1=read.csv("D:/memd_fmld153_1_1118",header=TRUE,sep=',')
MEMD_FMLD_154_1=read.csv("D:/memd_fmld154_1_1118",header=TRUE,sep=',')
MEMD_FMLD_161_1=read.csv("D:/memd_fmld161_1_1118",header=TRUE,sep=',')
MEMD_FMLD_162_1=read.csv("D:/memd_fmld162_1_1118",header=TRUE,sep=',')
MEMD_FMLD_163_1=read.csv("D:/memd_fmld163_1_1118",header=TRUE,sep=',')
MEMD_FMLD_164_1=read.csv("D:/memd_fmld164_1_1118",header=TRUE,sep=',')
MEMD_FMLD_171_1=read.csv("D:/memd_fmld171_1_1118",header=TRUE,sep=',')
MEMD_FMLD_172_1=read.csv("D:/memd_fmld172_1_1118",header=TRUE,sep=',')
MEMD_FMLD_173_1=read.csv("D:/memd_fmld173_1_1118",header=TRUE,sep=',')
MEMD_FMLD_174_1=read.csv("D:/memd_fmld174_1_1118",header=TRUE,sep=',')

```

```{r}
MEMD_FMLD_141_1=read.csv("E:/memd_fmld141_1_1118",header=TRUE,sep=',')
MEMD_FMLD_142_1=read.csv("E:/memd_fmld142_1_1118",header=TRUE,sep=',')
MEMD_FMLD_143_1=read.csv("E:/memd_fmld143_1_1118",header=TRUE,sep=',')
MEMD_FMLD_144_1=read.csv("E:/memd_fmld144_1_1118",header=TRUE,sep=',')
MEMD_FMLD_151_1=read.csv("E:/memd_fmld151_1_1118",header=TRUE,sep=',')
MEMD_FMLD_152_1=read.csv("E:/memd_fmld152_1_1118",header=TRUE,sep=',')
MEMD_FMLD_153_1=read.csv("E:/memd_fmld153_1_1118",header=TRUE,sep=',')
MEMD_FMLD_154_1=read.csv("E:/memd_fmld154_1_1118",header=TRUE,sep=',')
MEMD_FMLD_161_1=read.csv("E:/memd_fmld161_1_1118",header=TRUE,sep=',')
MEMD_FMLD_162_1=read.csv("E:/memd_fmld162_1_1118",header=TRUE,sep=',')
MEMD_FMLD_163_1=read.csv("E:/memd_fmld163_1_1118",header=TRUE,sep=',')
MEMD_FMLD_164_1=read.csv("E:/memd_fmld164_1_1118",header=TRUE,sep=',')
MEMD_FMLD_171_1=read.csv("E:/memd_fmld171_1_1118",header=TRUE,sep=',')
MEMD_FMLD_172_1=read.csv("E:/memd_fmld172_1_1118",header=TRUE,sep=',')
MEMD_FMLD_173_1=read.csv("E:/memd_fmld173_1_1118",header=TRUE,sep=',')
MEMD_FMLD_174_1=read.csv("E:/memd_fmld174_1_1118",header=TRUE,sep=',')
```


```{r}
MEMD_FMLD_141_1=read.csv("F:/memd_fmld141_1_1118",header=TRUE,sep=',')
MEMD_FMLD_142_1=read.csv("F:/memd_fmld142_1_1118",header=TRUE,sep=',')
MEMD_FMLD_143_1=read.csv("F:/memd_fmld143_1_1118",header=TRUE,sep=',')
MEMD_FMLD_144_1=read.csv("F:/memd_fmld144_1_1118",header=TRUE,sep=',')
MEMD_FMLD_151_1=read.csv("F:/memd_fmld151_1_1118",header=TRUE,sep=',')
MEMD_FMLD_152_1=read.csv("F:/memd_fmld152_1_1118",header=TRUE,sep=',')
MEMD_FMLD_153_1=read.csv("F:/memd_fmld153_1_1118",header=TRUE,sep=',')
MEMD_FMLD_154_1=read.csv("F:/memd_fmld154_1_1118",header=TRUE,sep=',')
MEMD_FMLD_161_1=read.csv("F:/memd_fmld161_1_1118",header=TRUE,sep=',')
MEMD_FMLD_162_1=read.csv("F:/memd_fmld162_1_1118",header=TRUE,sep=',')
MEMD_FMLD_163_1=read.csv("F:/memd_fmld163_1_1118",header=TRUE,sep=',')
MEMD_FMLD_164_1=read.csv("F:/memd_fmld164_1_1118",header=TRUE,sep=',')
MEMD_FMLD_171_1=read.csv("F:/memd_fmld171_1_1118",header=TRUE,sep=',')
MEMD_FMLD_172_1=read.csv("F:/memd_fmld172_1_1118",header=TRUE,sep=',')
MEMD_FMLD_173_1=read.csv("F:/memd_fmld173_1_1118",header=TRUE,sep=',')
MEMD_FMLD_174_1=read.csv("F:/memd_fmld174_1_1118",header=TRUE,sep=',')
```


```{r}
names(MEMD_FMLD_141_1)
ncol(MEMD_FMLD_141_1)
```

```{r}
MEMD_FMLD_141_1$ANFEDTXM <- NULL
MEMD_FMLD_141_1$ANFEDTXX <- NULL
MEMD_FMLD_141_1$ANFE_TXM <- NULL
MEMD_FMLD_141_1$ANFE_TXX <- NULL
MEMD_FMLD_141_1$ANSTATXM <- NULL
MEMD_FMLD_141_1$ANSTATXX <- NULL
MEMD_FMLD_141_1$ANST_TXM <- NULL
MEMD_FMLD_141_1$ANST_TXX <- NULL
MEMD_FMLD_141_1$FEDTXX  <- NULL
MEMD_FMLD_141_1$FEDTXX_ <- NULL
MEMD_FMLD_141_1$STATXX  <- NULL
MEMD_FMLD_141_1$STATXX_ <- NULL

names(MEMD_FMLD_141_1)
ncol(MEMD_FMLD_141_1)
```

```{r}
MEMD_FMLD_142_1$ANFEDTXM <- NULL
MEMD_FMLD_142_1$ANFEDTXX <- NULL
MEMD_FMLD_142_1$ANFE_TXM <- NULL
MEMD_FMLD_142_1$ANFE_TXX <- NULL
MEMD_FMLD_142_1$ANSTATXM <- NULL
MEMD_FMLD_142_1$ANSTATXX <- NULL
MEMD_FMLD_142_1$ANST_TXM <- NULL
MEMD_FMLD_142_1$ANST_TXX <- NULL
MEMD_FMLD_142_1$FEDTXX  <- NULL
MEMD_FMLD_142_1$FEDTXX_ <- NULL
MEMD_FMLD_142_1$STATXX  <- NULL
MEMD_FMLD_142_1$STATXX_ <- NULL

names(MEMD_FMLD_142_1)
ncol(MEMD_FMLD_142_1)
```

```{r}
MEMD_FMLD_143_1$ANFEDTXM <- NULL
MEMD_FMLD_143_1$ANFEDTXX <- NULL
MEMD_FMLD_143_1$ANFE_TXM <- NULL
MEMD_FMLD_143_1$ANFE_TXX <- NULL
MEMD_FMLD_143_1$ANSTATXM <- NULL
MEMD_FMLD_143_1$ANSTATXX <- NULL
MEMD_FMLD_143_1$ANST_TXM <- NULL
MEMD_FMLD_143_1$ANST_TXX <- NULL
MEMD_FMLD_143_1$FEDTXX  <- NULL
MEMD_FMLD_143_1$FEDTXX_ <- NULL
MEMD_FMLD_143_1$STATXX  <- NULL
MEMD_FMLD_143_1$STATXX_ <- NULL

names(MEMD_FMLD_143_1)
ncol(MEMD_FMLD_143_1)
```

```{r}
MEMD_FMLD_144_1$ANFEDTXM <- NULL
MEMD_FMLD_144_1$ANFEDTXX <- NULL
MEMD_FMLD_144_1$ANFE_TXM <- NULL
MEMD_FMLD_144_1$ANFE_TXX <- NULL
MEMD_FMLD_144_1$ANSTATXM <- NULL
MEMD_FMLD_144_1$ANSTATXX <- NULL
MEMD_FMLD_144_1$ANST_TXM <- NULL
MEMD_FMLD_144_1$ANST_TXX <- NULL
MEMD_FMLD_144_1$FEDTXX  <- NULL
MEMD_FMLD_144_1$FEDTXX_ <- NULL
MEMD_FMLD_144_1$STATXX  <- NULL
MEMD_FMLD_144_1$STATXX_ <- NULL

names(MEMD_FMLD_144_1)
ncol(MEMD_FMLD_144_1)
```

```{r}
MEMD_FMLD_141_2=read.csv("D:/memd_fmld141_2_1118",header=TRUE,sep=',')
MEMD_FMLD_142_2=read.csv("D:/memd_fmld142_2_1118",header=TRUE,sep=',')
MEMD_FMLD_143_2=read.csv("D:/memd_fmld143_2_1118",header=TRUE,sep=',')
MEMD_FMLD_144_2=read.csv("D:/memd_fmld144_2_1118",header=TRUE,sep=',')
MEMD_FMLD_151_2=read.csv("D:/memd_fmld151_2_1118",header=TRUE,sep=',')
MEMD_FMLD_152_2=read.csv("D:/memd_fmld152_2_1118",header=TRUE,sep=',')
MEMD_FMLD_153_2=read.csv("D:/memd_fmld153_2_1118",header=TRUE,sep=',')
MEMD_FMLD_154_2=read.csv("D:/memd_fmld154_2_1118",header=TRUE,sep=',')
MEMD_FMLD_161_2=read.csv("D:/memd_fmld161_2_1118",header=TRUE,sep=',')
MEMD_FMLD_162_2=read.csv("D:/memd_fmld162_2_1118",header=TRUE,sep=',')
MEMD_FMLD_163_2=read.csv("D:/memd_fmld163_2_1118",header=TRUE,sep=',')
MEMD_FMLD_164_2=read.csv("D:/memd_fmld164_2_1118",header=TRUE,sep=',')
MEMD_FMLD_171_2=read.csv("D:/memd_fmld171_2_1118",header=TRUE,sep=',')
MEMD_FMLD_172_2=read.csv("D:/memd_fmld172_2_1118",header=TRUE,sep=',')
MEMD_FMLD_173_2=read.csv("D:/memd_fmld173_2_1118",header=TRUE,sep=',')
MEMD_FMLD_174_2=read.csv("D:/memd_fmld174_2_1118",header=TRUE,sep=',')
```

```{r}
MEMD_FMLD_141_2=read.csv("E:/memd_fmld141_2_1118",header=TRUE,sep=',')
MEMD_FMLD_142_2=read.csv("E:/memd_fmld142_2_1118",header=TRUE,sep=',')
MEMD_FMLD_143_2=read.csv("E:/memd_fmld143_2_1118",header=TRUE,sep=',')
MEMD_FMLD_144_2=read.csv("E:/memd_fmld144_2_1118",header=TRUE,sep=',')
MEMD_FMLD_151_2=read.csv("E:/memd_fmld151_2_1118",header=TRUE,sep=',')
MEMD_FMLD_152_2=read.csv("E:/memd_fmld152_2_1118",header=TRUE,sep=',')
MEMD_FMLD_153_2=read.csv("E:/memd_fmld153_2_1118",header=TRUE,sep=',')
MEMD_FMLD_154_2=read.csv("E:/memd_fmld154_2_1118",header=TRUE,sep=',')
MEMD_FMLD_161_2=read.csv("E:/memd_fmld161_2_1118",header=TRUE,sep=',')
MEMD_FMLD_162_2=read.csv("E:/memd_fmld162_2_1118",header=TRUE,sep=',')
MEMD_FMLD_163_2=read.csv("E:/memd_fmld163_2_1118",header=TRUE,sep=',')
MEMD_FMLD_164_2=read.csv("E:/memd_fmld164_2_1118",header=TRUE,sep=',')
MEMD_FMLD_171_2=read.csv("E:/memd_fmld171_2_1118",header=TRUE,sep=',')
MEMD_FMLD_172_2=read.csv("E:/memd_fmld172_2_1118",header=TRUE,sep=',')
MEMD_FMLD_173_2=read.csv("E:/memd_fmld173_2_1118",header=TRUE,sep=',')
MEMD_FMLD_174_2=read.csv("E:/memd_fmld174_2_1118",header=TRUE,sep=',')
```


```{r}
MEMD_FMLD_141_2=read.csv("F:/memd_fmld141_2_1118",header=TRUE,sep=',')
MEMD_FMLD_142_2=read.csv("F:/memd_fmld142_2_1118",header=TRUE,sep=',')
MEMD_FMLD_143_2=read.csv("F:/memd_fmld143_2_1118",header=TRUE,sep=',')
MEMD_FMLD_144_2=read.csv("F:/memd_fmld144_2_1118",header=TRUE,sep=',')
MEMD_FMLD_151_2=read.csv("F:/memd_fmld151_2_1118",header=TRUE,sep=',')
MEMD_FMLD_152_2=read.csv("F:/memd_fmld152_2_1118",header=TRUE,sep=',')
MEMD_FMLD_153_2=read.csv("F:/memd_fmld153_2_1118",header=TRUE,sep=',')
MEMD_FMLD_154_2=read.csv("F:/memd_fmld154_2_1118",header=TRUE,sep=',')
MEMD_FMLD_161_2=read.csv("F:/memd_fmld161_2_1118",header=TRUE,sep=',')
MEMD_FMLD_162_2=read.csv("F:/memd_fmld162_2_1118",header=TRUE,sep=',')
MEMD_FMLD_163_2=read.csv("F:/memd_fmld163_2_1118",header=TRUE,sep=',')
MEMD_FMLD_164_2=read.csv("F:/memd_fmld164_2_1118",header=TRUE,sep=',')
MEMD_FMLD_171_2=read.csv("F:/memd_fmld171_2_1118",header=TRUE,sep=',')
MEMD_FMLD_172_2=read.csv("F:/memd_fmld172_2_1118",header=TRUE,sep=',')
MEMD_FMLD_173_2=read.csv("F:/memd_fmld173_2_1118",header=TRUE,sep=',')
MEMD_FMLD_174_2=read.csv("F:/memd_fmld174_2_1118",header=TRUE,sep=',')
```


```{r}
ncol(MEMD_FMLD_141_2)
ncol(MEMD_FMLD_142_2)
ncol(MEMD_FMLD_143_2)
ncol(MEMD_FMLD_144_2)
ncol(MEMD_FMLD_151_2)
ncol(MEMD_FMLD_152_2)
ncol(MEMD_FMLD_153_2)
ncol(MEMD_FMLD_154_2)
ncol(MEMD_FMLD_161_2)
ncol(MEMD_FMLD_162_2)
ncol(MEMD_FMLD_163_2)
ncol(MEMD_FMLD_164_2)
ncol(MEMD_FMLD_171_2)
ncol(MEMD_FMLD_172_2)
ncol(MEMD_FMLD_173_2)
ncol(MEMD_FMLD_174_2)
```

```{r}
MEMD_FMLD_141_2$ANFEDTXM <- NULL
MEMD_FMLD_141_2$ANFEDTXX <- NULL
MEMD_FMLD_141_2$ANFE_TXM <- NULL
MEMD_FMLD_141_2$ANFE_TXX <- NULL
MEMD_FMLD_141_2$ANSTATXM <- NULL
MEMD_FMLD_141_2$ANSTATXX <- NULL
MEMD_FMLD_141_2$ANST_TXM <- NULL
MEMD_FMLD_141_2$ANST_TXX <- NULL
MEMD_FMLD_141_2$FEDTXX <- NULL
MEMD_FMLD_141_2$FEDTXX_ <- NULL
MEMD_FMLD_141_2$STATXX <- NULL
MEMD_FMLD_141_2$STATXX_ <- NULL

names(MEMD_FMLD_141_2)
ncol(MEMD_FMLD_141_2)

```

```{r}
MEMD_FMLD_142_2$ANFEDTXM <- NULL
MEMD_FMLD_142_2$ANFEDTXX <- NULL
MEMD_FMLD_142_2$ANFE_TXM <- NULL
MEMD_FMLD_142_2$ANFE_TXX <- NULL
MEMD_FMLD_142_2$ANSTATXM <- NULL
MEMD_FMLD_142_2$ANSTATXX <- NULL
MEMD_FMLD_142_2$ANST_TXM <- NULL
MEMD_FMLD_142_2$ANST_TXX <- NULL
MEMD_FMLD_142_2$FEDTXX <- NULL
MEMD_FMLD_142_2$FEDTXX_ <- NULL
MEMD_FMLD_142_2$STATXX <- NULL
MEMD_FMLD_142_2$STATXX_ <- NULL

names(MEMD_FMLD_142_2)
ncol(MEMD_FMLD_142_2)
```

```{r}
MEMD_FMLD_143_2$ANFEDTXM <- NULL
MEMD_FMLD_143_2$ANFEDTXX <- NULL
MEMD_FMLD_143_2$ANFE_TXM <- NULL
MEMD_FMLD_143_2$ANFE_TXX <- NULL
MEMD_FMLD_143_2$ANSTATXM <- NULL
MEMD_FMLD_143_2$ANSTATXX <- NULL
MEMD_FMLD_143_2$ANST_TXM <- NULL
MEMD_FMLD_143_2$ANST_TXX <- NULL
MEMD_FMLD_143_2$FEDTXX <- NULL
MEMD_FMLD_143_2$FEDTXX_ <- NULL
MEMD_FMLD_143_2$STATXX <- NULL
MEMD_FMLD_143_2$STATXX_ <- NULL

names(MEMD_FMLD_143_2)
ncol(MEMD_FMLD_143_2)
```


```{r}
MEMD_FMLD_144_2$ANFEDTXM <- NULL
MEMD_FMLD_144_2$ANFEDTXX <- NULL
MEMD_FMLD_144_2$ANFE_TXM <- NULL
MEMD_FMLD_144_2$ANFE_TXX <- NULL
MEMD_FMLD_144_2$ANSTATXM <- NULL
MEMD_FMLD_144_2$ANSTATXX <- NULL
MEMD_FMLD_144_2$ANST_TXM <- NULL
MEMD_FMLD_144_2$ANST_TXX <- NULL
MEMD_FMLD_144_2$FEDTXX <- NULL
MEMD_FMLD_144_2$FEDTXX_ <- NULL
MEMD_FMLD_144_2$STATXX <- NULL
MEMD_FMLD_144_2$STATXX_ <- NULL

names(MEMD_FMLD_144_2)
ncol(MEMD_FMLD_144_2)
```


```{r}
MEMD_FMLD_2_train <- rbind.data.frame(MEMD_FMLD_141_2,MEMD_FMLD_142_2,MEMD_FMLD_143_2,MEMD_FMLD_144_2,
      MEMD_FMLD_151_2,MEMD_FMLD_152_2,MEMD_FMLD_153_2,MEMD_FMLD_154_2,
      MEMD_FMLD_161_2,MEMD_FMLD_162_2,MEMD_FMLD_163_2,MEMD_FMLD_164_2
      )
```


```{r}
MEMD_FMLD_2_train <- rbind.data.frame(
      MEMD_FMLD_151_2,MEMD_FMLD_152_2,MEMD_FMLD_153_2,MEMD_FMLD_154_2,
      MEMD_FMLD_161_2,MEMD_FMLD_162_2,MEMD_FMLD_163_2,MEMD_FMLD_164_2
      )
```

```{r}
MEMD_FMLD_2_train <- rbind.data.frame(MEMD_FMLD_161_2,MEMD_FMLD_162_2,MEMD_FMLD_163_2,MEMD_FMLD_164_2)
```

```{r}
MEMD_FMLD_2_train$WAGEX_2 = "Y"
MEMD_FMLD_2_train$WAGEX_2[MEMD_FMLD_2_train$WAGEX_ == "C"] = "N"
MEMD_FMLD_2_train$WAGEX_2 = as.factor(MEMD_FMLD_2_train$WAGEX_2)
MEMD_FMLD_2_train$WAGEX_2 = relevel(MEMD_FMLD_2_train$WAGEX_2,"N")
table(MEMD_FMLD_2_train$WAGEX_,MEMD_FMLD_2_train$WAGEX_2)
summary(MEMD_FMLD_2_train$WAGEX_2)
```

```{r}
MEMD_FMLD_2_train$WAGEX_3 = "Y"
MEMD_FMLD_2_train$WAGEX_3[MEMD_FMLD_2_train$WAGEX_ == "C"] = "N"
MEMD_FMLD_2_train$WAGEX_3[MEMD_FMLD_2_train$WAGEX_ == "B"] = "N"
MEMD_FMLD_2_train$WAGEX_3 = as.factor(MEMD_FMLD_2_train$WAGEX_3)
MEMD_FMLD_2_train$WAGEX_3 = relevel(MEMD_FMLD_2_train$WAGEX_3,"N")
table(MEMD_FMLD_2_train$WAGEX_,MEMD_FMLD_2_train$WAGEX_3)
summary(MEMD_FMLD_2_train$WAGEX_3)
```

```{r}
MEMD_FMLD_2_test <- rbind.data.frame(MEMD_FMLD_171_2,MEMD_FMLD_172_2,MEMD_FMLD_173_2,MEMD_FMLD_174_2)
```

```{r}
MEMD_FMLD_2_test$WAGEX_2 = "Y"
MEMD_FMLD_2_test$WAGEX_2[MEMD_FMLD_2_test$WAGEX_ == "C"] = "N"
MEMD_FMLD_2_test$WAGEX_2 = as.factor(MEMD_FMLD_2_test$WAGEX_2)
MEMD_FMLD_2_test$WAGEX_2 = relevel(MEMD_FMLD_2_test$WAGEX_2,"N")
table(MEMD_FMLD_2_test$WAGEX_,MEMD_FMLD_2_test$WAGEX_2)
summary(MEMD_FMLD_2_test$WAGEX_2)
```

```{r}
MEMD_FMLD_2_test$WAGEX_3 = "Y"
MEMD_FMLD_2_test$WAGEX_3[MEMD_FMLD_2_test$WAGEX_ == "C"] = "N"
MEMD_FMLD_2_test$WAGEX_3[MEMD_FMLD_2_test$WAGEX_ == "B"] = "N"
MEMD_FMLD_2_test$WAGEX_3 = as.factor(MEMD_FMLD_2_test$WAGEX_3)
MEMD_FMLD_2_test$WAGEX_3 = relevel(MEMD_FMLD_2_test$WAGEX_3,"N")
table(MEMD_FMLD_2_test$WAGEX_,MEMD_FMLD_2_test$WAGEX_3)
summary(MEMD_FMLD_2_test$WAGEX_3)
```

```{r}
WAGEX_tree1 <- rpart(WAGEX_ ~ CUTENURE + DESCRIP + VEHQ + TYPOWND + EARNCOMP + ARM_FORC + MARITAL + AGE + WKSTATUS, data = MEMD_FMLD_2_train, method = "class")
WAGEX_tree1

```


```{r}
WAGEX_2tree1 <- rpart(WAGEX_2 ~ CUTENURE + DESCRIP + VEHQ + TYPOWND + EARNCOMP + ARM_FORC + MARITAL + AGE + WKSTATUS + EMPLTYPE + CU_CODE1 + EDUCA + MEMBRACE + OCCULIST + HRSPERWK + GROSPAYX + OCCUEARN + HORIGIN + WAGEB + IN_COLL + MEDICARE, data = MEMD_FMLD_2_train, method = "class")
WAGEX_2tree1
```

```{r}
WAGEX_3tree1 <- rpart(WAGEX_3 ~ CUTENURE + DESCRIP + VEHQ + TYPOWND + EARNCOMP + ARM_FORC + MARITAL + AGE + WKSTATUS + EMPLTYPE + CU_CODE1 + EDUCA + MEMBRACE + OCCULIST + HRSPERWK + GROSPAYX + OCCUEARN + HORIGIN + WAGEB + IN_COLL + MEDICARE, data = MEMD_FMLD_2_train, method = "class")
WAGEX_3tree1
```


```{r}
party_WAGEX_tree1 <- as.party(WAGEX_tree1)
plot(party_WAGEX_tree1, gp = gpar(fontsize = 9))
```


```{r}
party_WAGEX_2tree1 <- as.party(WAGEX_2tree1)
plot(party_WAGEX_2tree1, gp = gpar(fontsize = 9))
```

```{r}
party_WAGEX_3tree1 <- as.party(WAGEX_3tree1)
plot(party_WAGEX_3tree1, gp = gpar(fontsize = 9))
```


##Add in these variables to the first tree and you end up with 
##just one node, rather as we see for the second tree:
##
##EMPLTYPE + CU_CODE1 + EDUCA + MEMBRACE + OCCULIST + HRSPERWK


```{r}
WAGEX_2tree2 <- rpart(WAGEX_2 ~ CUTENURE + VEHQ + TYPOWND + EARNCOMP + ARM_FORC + MARITAL + AGE + WKSTATUS + EMPLTYPE + CU_CODE1 + EDUCA + MEMBRACE + OCCULIST + HRSPERWK + HORIGIN + GROSPAYX + MEDICARE + OCCUEARN + WAGEB + IN_COLL + DESCRIP, data = MEMD_FMLD_2_train, 
                     control = rpart.control(minsplit = 10,                                            minbucket = 3, 
                     cp = 0.001, # min improvement through splitting
                     maxdepth = 30,
                     method = "class"))
```

```{r}
WAGEX_3tree2 <- rpart(WAGEX_3 ~ CUTENURE + VEHQ + TYPOWND + EARNCOMP + ARM_FORC + MARITAL + AGE + WKSTATUS + EMPLTYPE + CU_CODE1 + EDUCA + MEMBRACE + OCCULIST + HRSPERWK + HORIGIN + GROSPAYX + MEDICARE + OCCUEARN + WAGEB + IN_COLL + DESCRIP, data = MEMD_FMLD_2_train, 
                     control = rpart.control(minsplit = 10,                                            minbucket = 3, 
                     cp = 0.001, # min improvement through splitting
                     maxdepth = 30,
                     method = "class"))
```

```{r}
party_WAGEX_2tree2 <- as.party(WAGEX_2tree2)
plot(party_WAGEX_2tree2, gp = gpar(fontsize = 6))
```

```{r}
party_WAGEX_3tree2 <- as.party(WAGEX_3tree2)
plot(party_WAGEX_3tree2, gp = gpar(fontsize = 6))
```

```{r}
printcp(WAGEX_2tree2)
plotcp(WAGEX_2tree2)
```

```{r}
minx2 <- which.min(WAGEX_2tree2$cptable[,"xerror"])
mincp2a <- WAGEX_2tree2$cptable[minx2,"CP"]
mincp2a
```

```{r}
minx2 <- which.min(WAGEX_2tree2$cptable[,"xerror"])
minxse2 <- WAGEX_2tree2$cptable[minx2,"xerror"] + WAGEX_2tree2$cptable[minx2,"xstd"]
minse2 <- which(WAGEX_2tree2$cptable[1:minx2,"xerror"] < minxse2)
mincp2b <- WAGEX_2tree2$cptable[minse2[1],"CP"]
mincp2b
```

```{r}
pruned_WAGEX_2tree2_scv <- prune(WAGEX_2tree2, cp = mincp2a)
pruned_WAGEX_2tree2_scv
```

```{r}
pruned_WAGEX_2tree2_1SE <- prune(WAGEX_2tree2, cp = mincp2b)
pruned_WAGEX_2tree2_1SE
```
##The 2 WAGEX_2 trees once showed indistinguishable...
##Move on now to the WAGEX_3 outcome variable analysis
##Plotting the smaller tree in the WAGEX_2 Response...As seen here it is not so helpful...Same for CART generally

```{r}
party_pruned_WAGEX_2tree2_1SE <- as.party(pruned_WAGEX_2tree2_1SE)
plot(party_pruned_WAGEX_2tree2_1SE, gp = gpar(fontsize = 7))
```


```{r}
printcp(WAGEX_3tree2)
plotcp(WAGEX_3tree2)
```

```{r}
minx3 <- which.min(WAGEX_3tree2$cptable[,"xerror"])
mincp3a <- WAGEX_3tree2$cptable[minx3,"CP"]
mincp3a
```

```{r}
minx3 <- which.min(WAGEX_3tree2$cptable[,"xerror"])
minxse3 <- WAGEX_3tree2$cptable[minx3,"xerror"] + WAGEX_3tree2$cptable[minx3,"xstd"]
minse3 <- which(WAGEX_3tree2$cptable[1:minx3,"xerror"] < minxse3)
mincp3b <- WAGEX_3tree2$cptable[minse3[1],"CP"]
mincp3b
```

```{r}
pruned_WAGEX_3tree2_scv <- prune(WAGEX_3tree2, cp = mincp3a)
pruned_WAGEX_3tree2_scv
```

```{r}
pruned_WAGEX_3tree2_1SE <- prune(WAGEX_3tree2, cp = mincp3b)
pruned_WAGEX_3tree2_1SE
```

##plotting the smaller tree for the WAGEX_3 Response
```{r}
party_pruned_WAGEX_3tree2_1SE <- as.party(pruned_WAGEX_3tree2_1SE)
plot(party_pruned_WAGEX_3tree2_1SE, gp = gpar(fontsize = 7))

```

```{r}
y_tree_scv <- predict(pruned_WAGEX_3tree2_scv, newdata = MEMD_FMLD_2_test, type = "class")
y_tree_1SE <- predict(pruned_WAGEX_3tree2_1SE, newdata = MEMD_FMLD_2_test, type = "class")
```


```{r}
confusionMatrix(y_tree_scv, MEMD_FMLD_2_test$WAGEX_3, mode = "everything", positive = "N")
confusionMatrix(y_tree_1SE, MEMD_FMLD_2_test$WAGEX_3, mode = "everything", positive = "N")
```

###Let's do an RF on this stuff
###We burn so much computing power, we need to makes things small

```{r}
MEMD_FMLD_2_train <- rbind.data.frame(MEMD_FMLD_161_2,MEMD_FMLD_162_2,MEMD_FMLD_163_2,MEMD_FMLD_164_2)

MEMD_FMLD_2_train$WAGEX_2 = "Y"
MEMD_FMLD_2_train$WAGEX_2[MEMD_FMLD_2_train$WAGEX_ == "C"] = "N"
MEMD_FMLD_2_train$WAGEX_2 = as.factor(MEMD_FMLD_2_train$WAGEX_2)
MEMD_FMLD_2_train$WAGEX_2 = relevel(MEMD_FMLD_2_train$WAGEX_2,"N")
table(MEMD_FMLD_2_train$WAGEX_2,MEMD_FMLD_2_train$WAGEX_2)
summary(MEMD_FMLD_2_train$WAGEX_2)

MEMD_FMLD_2_train$WAGEX_3 = "Y"
MEMD_FMLD_2_train$WAGEX_3[MEMD_FMLD_2_train$WAGEX_ == "C"] = "N"
MEMD_FMLD_2_train$WAGEX_3[MEMD_FMLD_2_train$WAGEX_ == "B"] = "N"
MEMD_FMLD_2_train$WAGEX_3 = as.factor(MEMD_FMLD_2_train$WAGEX_3)
MEMD_FMLD_2_train$WAGEX_3 = relevel(MEMD_FMLD_2_train$WAGEX_3,"N")
table(MEMD_FMLD_2_train$WAGEX_,MEMD_FMLD_2_train$WAGEX_3)
summary(MEMD_FMLD_2_train$WAGEX_3)

MEMD_FMLD_2_train$WAGEX_1 = "D"
MEMD_FMLD_2_train$WAGEX_1[MEMD_FMLD_2_train$WAGEX_ == "B"] = "B"
MEMD_FMLD_2_train$WAGEX_1[MEMD_FMLD_2_train$WAGEX_ == "C"] = "C"
MEMD_FMLD_2_train$WAGEX_1 = as.factor(MEMD_FMLD_2_train$WAGEX_1)
table(MEMD_FMLD_2_train$WAGEX_,MEMD_FMLD_2_train$WAGEX_1)
summary(MEMD_FMLD_2_train$WAGEX_1)

MEMD_FMLD_2_test$WAGEX_1 = "D"
MEMD_FMLD_2_test$WAGEX_1[MEMD_FMLD_2_test$WAGEX_ == "B"] = "B"
MEMD_FMLD_2_test$WAGEX_1[MEMD_FMLD_2_test$WAGEX_ == "C"] = "C"
MEMD_FMLD_2_test$WAGEX_1 = as.factor(MEMD_FMLD_2_test$WAGEX_1)
table(MEMD_FMLD_2_test$WAGEX_,MEMD_FMLD_2_test$WAGEX_1)
summary(MEMD_FMLD_2_test$WAGEX_1)


```

```{r}
X1 = subset(MEMD_FMLD_2_train, select = c(WAGEX_,
                                          WAGEX_1,
                                           WAGEX_2,
                                           WAGEX_3,
                                           ARM_FORC,
                                           TYPOWND,
                                           IN_COLL,
                                           DESCRIP,
                                           WAGEB,
                                           GROSPAYX,
                                           MEDICARE,
                                           VEHQ,
                                           CU_CODE1,
                                           CUTENURE,
                                           HRSPERWK,
                                           AGE,
                                           OCCUEARN,
                                           EDUCA,
                                           HORIGIN,
                                           EARNCOMP,
                                           MEMBRACE,
                                           EMPLTYPE,
                                           WKSTATUS,
                                           OCCULIST,
                                           MARITAL
                                           ))

```

```{r}
X1$GROSPAYX <- as.numeric(X1$GROSPAYX)
X1$AGE <- as.numeric(X1$AGE)
X1$HRSPERWK <- as.numeric(X1$HRSPERWK)
X1$OCCUEARN <- as.factor(X1$OCCUEARN)
X1$ARM_FORC <- as.factor(X1$ARM_FORC)
X1$TYPOWND <- as.factor(X1$TYPOWND)
X1$IN_COLL <- as.factor(X1$IN_COLL)
X1$DESCRIP <- as.factor(X1$DESCRIP)
X1$WAGEB <- as.factor(X1$WAGEB)
X1$MEDICARE <- as.factor(X1$MEDICARE)
X1$VEHQ <- as.factor(X1$VEHQ)
X1$CU_CODE1 <- as.factor(X1$CU_CODE1)
X1$CUTENURE <- as.factor(X1$CUTENURE)
X1$EDUCA <- as.factor(X1$EDUCA)
X1$HORIGIN <- as.factor(X1$HORIGIN)
X1$EARNCOMP <- as.factor(X1$EARNCOMP)
X1$MEMBRACE <- as.factor(X1$MEMBRACE)
X1$EMPLTYPE <- as.factor(X1$EMPLTYPE)
X1$WKSTATUS <- as.factor(X1$WKSTATUS)
X1$OCCULIST <- as.factor(X1$OCCULIST)
X1$MARITAL <- as.factor(X1$MARITAL)
```

```{r}
levels(X1$OCCUEARN)
table(is.na(X1$OCCUEARN))
```

```{r}
levels(X1$EARNCOMP) <- c(levels(X1$EARNCOMP), "8")
levels(X1$DESCRIP) <- c(levels(X1$DESCRIP), "4","8")
levels(X1$VEHQ) <- c(levels(X1$VEHQ), "13")
```

```{r}
table(is.na(X1$GROSPAYX))
table(is.na(X1$AGE))
table(is.na(X1$HRSPERWK))
table(is.na(X1$OCCUEARN))
table(is.na(X1$ARM_FORC))
table(is.na(X1$CUTENURE))
table(is.na(X1$EDUCA))
table(is.na(X1$HORIGIN))
table(is.na(X1$OCCULIST))
table(is.na(X1$MARITAL))
table(is.na(X1$WKSTATUS))
table(is.na(X1$TYPOWND))
table(is.na(X1$IN_COLL))
table(is.na(X1$DESCRIP))
table(is.na(X1$WAGEB))
table(is.na(X1$MEDICARE))
table(is.na(X1$VEHQ))
table(is.na(X1$CU_CODE1))
table(is.na(X1$EARNCOMP))
table(is.na(X1$MEMBRACE))
table(is.na(X1$EMPLTYPE))
```

```{r}
X1$ARM_FORC<-addNA(X1$ARM_FORC, ifany = FALSE)
X1$TYPOWND<-addNA(X1$TYPOWND, ifany = FALSE)
X1$IN_COLL<-addNA(X1$IN_COLL, ifany = FALSE)
X1$DESCRIP<-addNA(X1$DESCRIP, ifany = FALSE)
X1$WAGEB<-addNA(X1$WAGEB, ifany = FALSE)
X1$MEDICARE<-addNA(X1$MEDICARE, ifany = FALSE)
X1$VEHQ<-addNA(X1$VEHQ, ifany = FALSE)
```

```{r}
summary(X1$ARM_FORC)
summary(X1$EARNCOMP)
summary(X1$TYPOWND)
summary(X1$IN_COLL)
summary(X1$DESCRIP)
summary(X1$WAGEB)
summary(X1$VEHQ)
summary(X1$CU_CODE1)
summary(X1$CUTENURE)
summary(X1$EDUCA)
summary(X1$HORIGIN)
summary(X1$EARNCOMP)
summary(X1$MEMBRACE)
summary(X1$EMPLTYPE)
summary(X1$WKSTATUS)
summary(X1$OCCULIST)
summary(X1$MARITAL)

```

```{r}
summary(X2$ARM_FORC)
summary(X2$EARNCOMP)
summary(X2$TYPOWND)
summary(X2$IN_COLL)
summary(X2$DESCRIP)
summary(X2$WAGEB)
summary(X2$VEHQ)
summary(X2$CU_CODE1)
summary(X2$CUTENURE)
summary(X2$EDUCA)
summary(X2$HORIGIN)
summary(X2$EARNCOMP)
summary(X2$MEMBRACE)
summary(X2$EMPLTYPE)
summary(X2$WKSTATUS)
summary(X2$OCCULIST)
summary(X2$MARITAL)
```






```{r}
X1$GROSPAYXFLAG<-"0"
X1$GROSPAYXFLAG[is.na(X1$GROSPAYX) == "TRUE"] <- "1"
X1$GROSPAYXFLAG<-as.factor(X1$GROSPAYXFLAG)
summary(X1$GROSPAYXFLAG)
```

```{r}
rough_X1 <- na.roughfix(X1)
```

```{r}
X2 = subset(MEMD_FMLD_2_test, select = c(WAGEX_,
                                         WAGEX_1,
                                           WAGEX_2,
                                           WAGEX_3,
                                           ARM_FORC,
                                           TYPOWND,
                                           IN_COLL,
                                           DESCRIP,
                                           WAGEB,
                                           GROSPAYX,
                                           MEDICARE,
                                           VEHQ,
                                           CU_CODE1,
                                           CUTENURE,
                                           HRSPERWK,
                                           AGE,
                                           OCCUEARN,
                                           EDUCA,
                                           HORIGIN,
                                           EARNCOMP,
                                           MEMBRACE,
                                           EMPLTYPE,
                                           WKSTATUS,
                                           OCCULIST,
                                           MARITAL
                                           ))

```

```{r}
X2$GROSPAYX <- as.numeric(X2$GROSPAYX)
X2$AGE <- as.numeric(X2$AGE)
X2$HRSPERWK <- as.numeric(X2$HRSPERWK)
X2$OCCUEARN <- as.factor(X2$OCCUEARN)
X2$ARM_FORC <- as.factor(X2$ARM_FORC)
X2$TYPOWND <- as.factor(X2$TYPOWND)
X2$IN_COLL <- as.factor(X2$IN_COLL)
X2$DESCRIP <- as.factor(X2$DESCRIP)
X2$WAGEB <- as.factor(X2$WAGEB)
X2$MEDICARE <- as.factor(X2$MEDICARE)
X2$VEHQ <- as.factor(X2$VEHQ)
X2$CU_CODE1 <- as.factor(X2$CU_CODE1)
X2$CUTENURE <- as.factor(X2$CUTENURE)
X2$EDUCA <- as.factor(X2$EDUCA)
X2$HORIGIN <- as.factor(X2$HORIGIN)
X2$EARNCOMP <- as.factor(X2$EARNCOMP)
X2$MEMBRACE <- as.factor(X2$MEMBRACE)
X2$EMPLTYPE <- as.factor(X2$EMPLTYPE)
X2$WKSTATUS <- as.factor(X2$WKSTATUS)
X2$OCCULIST <- as.factor(X2$OCCULIST)
X2$MARITAL <- as.factor(X2$MARITAL)

```

```{r}
levels(X2$VEHQ) <- c(levels(X2$VEHQ),"10","16","18")
```

```{r}
levels(X2$OCCUEARN)
table(is.na(X2$OCCUEARN))
```


```{r}
table(is.na(MEMD_FMLD_2_train$GROSPAYX))
table(is.na(MEMD_FMLD_2_train$AGE))
table(is.na(MEMD_FMLD_2_train$HRSPERWK))
table(is.na(MEMD_FMLD_2_train$OCCUEARN))
table(is.na(MEMD_FMLD_2_train$ARM_FORC))
table(is.na(MEMD_FMLD_2_train$CUTENURE))
table(is.na(MEMD_FMLD_2_train$EDUCA))
table(is.na(MEMD_FMLD_2_train$HORIGIN))
table(is.na(MEMD_FMLD_2_train$OCCULIST))
table(is.na(MEMD_FMLD_2_train$MARITAL))
table(is.na(MEMD_FMLD_2_train$WKSTATUS))
table(is.na(MEMD_FMLD_2_train$TYPOWND))
table(is.na(MEMD_FMLD_2_train$IN_COLL))
table(is.na(MEMD_FMLD_2_train$DESCRIP))
table(is.na(MEMD_FMLD_2_train$WAGEB))
table(is.na(MEMD_FMLD_2_train$MEDICARE))
table(is.na(MEMD_FMLD_2_train$VEHQ))
table(is.na(MEMD_FMLD_2_train$CU_CODE1))
table(is.na(MEMD_FMLD_2_train$EARNCOMP))
table(is.na(MEMD_FMLD_2_train$MEMBRACE))
table(is.na(MEMD_FMLD_2_train$EMPLTYPE))

```

```{r}
X2$ARM_FORC<-addNA(X2$ARM_FORC, ifany = FALSE)
X2$TYPOWND<-addNA(X2$TYPOWND, ifany = FALSE)
X2$IN_COLL<-addNA(X2$IN_COLL, ifany = FALSE)
X2$DESCRIP<-addNA(X2$DESCRIP, ifany = FALSE)
X2$WAGEB<-addNA(X2$WAGEB, ifany = FALSE)
X2$MEDICARE<-addNA(X2$MEDICARE, ifany = FALSE)
X2$VEHQ<-addNA(X2$VEHQ, ifany = FALSE)
```

```{r}
X2$GROSPAYXFLAG<-"0"
X2$GROSPAYXFLAG[is.na(X2$GROSPAYX) == "TRUE"] <- "1"
X2$GROSPAYXFLAG<-as.factor(X2$GROSPAYXFLAG)
summary(X2$GROSPAYXFLAG)
```

```{r}
rough_X2 <- na.roughfix(X2)
```

```{r}
ctrl <- trainControl(method = "cv",
                     number = 5,
                     summaryFunction = multiClassSummary,
                     classProbs = TRUE)
```

```{r}
grid <- expand.grid(mtry = c(5))
```

```{r}
set.seed(1000)
rf_rough_X1 <- train(WAGEX_3 ~ ARM_FORC + CU_CODE1 + CUTENURE + 
                       EARNCOMP + EDUCA + EMPLTYPE +
                       GROSPAYXFLAG + HORIGIN + IN_COLL + MARITAL +  
                       MEMBRACE + OCCULIST + TYPOWND +
                       VEHQ + WAGEB + WKSTATUS + AGE + GROSPAYX + 
                       HRSPERWK + OCCUEARN,
                       data = rough_X1,
                       method = "rf",
                       trControl = ctrl,
                       tuneGrid = grid,
                       metric = "ROC",
                       importance = TRUE,
                       proximity = TRUE)
```

```{r}
set.seed(1000)
rf_rough_X1b <- train(WAGEX_2 ~ ARM_FORC + CU_CODE1 + CUTENURE + 
                       EARNCOMP + EDUCA + EMPLTYPE +
                       GROSPAYXFLAG + HORIGIN + IN_COLL + MARITAL +  
                       MEMBRACE + OCCULIST + TYPOWND +
                       VEHQ + WAGEB + WKSTATUS + AGE + GROSPAYX + 
                       HRSPERWK + OCCUEARN,
                       data = rough_X1,
                       method = "rf",
                       trControl = ctrl,
                       tuneGrid = grid,
                       metric = "ROC",
                       importance = TRUE,
                       proximity = TRUE)
```

```{r}
install.packages("MLmetrics")
library(MLmetrics)
```


```{r}
set.seed(1000)
rf_rough_X1c <- train(WAGEX_1 ~ ARM_FORC + CU_CODE1 + CUTENURE + 
                       EARNCOMP + EDUCA + EMPLTYPE +
                       GROSPAYXFLAG + HORIGIN + IN_COLL + MARITAL +  
                       MEMBRACE + OCCULIST + TYPOWND +
                       VEHQ + WAGEB + WKSTATUS + AGE + GROSPAYX + 
                       HRSPERWK + OCCUEARN,
                       data = rough_X1,
                       method = "rf",
                       trControl = ctrl,
                       tuneGrid = grid,
                       metric = "ROC",
                       importance = TRUE,
                       proximity = TRUE)
```

```{r}
rf_rough_X1
```

```{r}
rf_rough_X1b
```

```{r}
rf_rough_X1c
```


```{r}
str(rf_rough_X1$finalModel)
```

```{r}
plot(rf_rough_X1$finalModel)
```

```{r}
str(rf_rough_X1$finalModel$proximity)
```

```{r}
rf_rough_X1$finalModel$proximity[1:10, 1:10]
```

```{r}
varImp(rf_rough_X1)
```

```{r}
plot(varImp(rf_rough_X1),top=15)
```

```{r}
c_rf <- predict(rf_rough_X1,newdata=rough_X2)
p_rf <- predict(rf_rough_X1,newdata=rough_X2,type="prob")
```


```{r}
confusionMatrix(c_rf,rough_X2$WAGEX_3)
```

```{r}
prob <- verify(pred = p_rf$N, obs=ifelse(rough_X2$WAGEX_3 == "N", 1, 0), frcst.type = "prob", obs.type = "binary")
```

```{r}
summary(prob)
```

```{r}
rf_roc <- roc(rough_X2$WAGEX_3, p_rf$N)
rf_roc
```

```{r}
plot(rf_roc)
```


##Now for WAGEX_2...
```{r}
plot(varImp(rf_rough_X1b),top=15)
```

```{r}
c_rfb <- predict(rf_rough_X1b,newdata=rough_X2)
p_rfb <- predict(rf_rough_X1b,newdata=rough_X2,type="prob")
```


```{r}
confusionMatrix(c_rfb,rough_X2$WAGEX_2)
```

```{r}
probb <- verify(pred = p_rfb$N, obs=ifelse(rough_X2$WAGEX_2 == "N", 1, 0), frcst.type = "prob", obs.type = "binary")
```

```{r}
summary(probb)
```

```{r}
rf_rocb <- roc(rough_X2$WAGEX_2, p_rf$N)
rf_rocb
```

```{r}
plot(rf_rocb)
```


##Now for WAGEX_1....

```{r}
plot(varImp(rf_rough_X1c),top=15)
postResample(pred=rf_rough_X1c,obs=rough_X2$WAGEX_1)

##c_rfc <- predict(rf_rough_X1c,newdata=rough_X2)
##p_rfc <- predict(rf_rough_X1c,newdata=rough_X2,type="prob")
##confusionMatrix(c_rfc,rough_X2$WAGEX_1)
##probc <- verify(pred = p_rfc$D, obs=ifelse(rough_X2$WAGEX_1 == "D", 1, 0), frcst.type = "prob", obs.type = "binary")
##summary(probc)
##rf_rocc<-roc(rough_X2$WAGEX_1, p_rfc$D)
##rf_rocc
```



##AdaBoost

```{r}
evalStats <- function(...) c(twoClassSummary(...),
                             defaultSummary(...),
                             mnLogLoss(...))
```

```{r}
ctrl2 <- trainControl(method="cv",
                     number=5,
                     summaryFunction=evalStats,
                     classProbs=TRUE)
```

```{r}
grid2 <- expand.grid(nIter=c(50,100,150),
                    method="Adaboost.M1")
```

```{r}
set.seed(1000)
Ada <- train(WAGEX_3 ~ ARM_FORC + CU_CODE1 + CUTENURE + 
                       EARNCOMP + EDUCA + EMPLTYPE +
                       GROSPAYXFLAG + HORIGIN + IN_COLL + MARITAL +  
                       MEMBRACE + OCCULIST + TYPOWND +
                       VEHQ + WAGEB + WKSTATUS + AGE + GROSPAYX + 
                       HRSPERWK + OCCUEARN,
  data = rough_X1,  
  method = "adaboost",
  trControl=ctrl2,
  tuneGrid=grid2,
  metric="logLoss")
```

```{r}
Ada
```

##GBM

```{r}
grid3<-expand.grid(interaction.depth=1:3,
                   n.trees=c(500,750,1000),
                   shrinkage=c(0.05,0.01),
                   n.minobsinnode=10)
```

```{r}
grid3
```

```{r}
set.seed(1000)
Gbm <- train(WAGEX_3 ~ ARM_FORC + CU_CODE1 + CUTENURE + 
                       EARNCOMP + EDUCA + EMPLTYPE +
                       GROSPAYXFLAG + HORIGIN + IN_COLL + MARITAL +  
                       MEMBRACE + OCCULIST + TYPOWND +
                       VEHQ + WAGEB + WKSTATUS + AGE + GROSPAYX + 
                       HRSPERWK + OCCUEARN,
             data=rough_X1,
             method="gbm",
             trControl=ctrl2,
             tuneGrid=grid3,
             metric="logLoss",
             distribution="bernoulli",
             verbose=FALSE)
```

```{r}
plot(Gbm)
```

```{r}
plot(varImp(Gbm),top=20)
```

##Following the pattern Chris established:  Compare with another CART (results should differ from above)
```{r}
grid4<-expand.grid(maxdepth=1:30)
```

```{r}
set.seed(1000)
Cart <- train(WAGEX_3 ~ ARM_FORC + CU_CODE1 + CUTENURE + 
                       EARNCOMP + EDUCA + EMPLTYPE +
                       GROSPAYXFLAG + HORIGIN + IN_COLL + MARITAL +  
                       MEMBRACE + OCCULIST + TYPOWND +
                       VEHQ + WAGEB + WKSTATUS + AGE + GROSPAYX + 
                       HRSPERWK + OCCUEARN,
             data=rough_X1,
             method="rpart2",
             trControl=ctrl2,
             tuneGrid=grid4,
             metric="logLoss")
```

```{r}
plot(Cart)
```

```{r}
Cart
```

```{r}
set.seed(1000)
Logit<-train(WAGEX_3 ~ ARM_FORC + CU_CODE1 + CUTENURE + 
                       EARNCOMP + EDUCA + EMPLTYPE +
                       GROSPAYXFLAG + HORIGIN + IN_COLL + MARITAL +  
                       MEMBRACE + OCCULIST + TYPOWND +
                       VEHQ + WAGEB + WKSTATUS + AGE + GROSPAYX + 
                       HRSPERWK + OCCUEARN,
             data=rough_X1,
             method="glm",
             trControl=ctrl2)
```

```{r}
summary(Logit)
```

```{r}
C_Ada <- predict(Ada, newdata=rough_X2)
C_Gbm <- predict(Gbm, newdata=rough_X2)
C_Cart <- predict(Cart, newdata=rough_X2)
C_Logit <- predict(Logit, newdata=rough_X2)

P_Ada <- predict(Ada, newdata=rough_X2, type="prob")
P_Gbm <- predict(Gbm, newdata=rough_X2, type="prob")
P_Cart <- predict(Cart, newdata=rough_X2, type="prob")
P_Logit <- predict(Logit, newdata=rough_X2, type="prob")

```

```{r}
postResample(pred=C_Ada,obs=rough_X2$WAGEX_3)
```

```{r}
postResample(pred=C_Gbm,obs=rough_X2$WAGEX_3)
```

```{r}
postResample(pred=C_Cart,obs=rough_X2$WAGEX_3)
```

```{r}
postResample(pred=C_Logit,obs=rough_X2$WAGEX_3)
```

```{r}
Ada_ROC <- roc(rough_X2$WAGEX_3, P_Ada$Y)
Gbm_ROC <- roc(rough_X2$WAGEX_3, P_Gbm$Y)
Cart_ROC <- roc(rough_X2$WAGEX_3, P_Cart$Y)
Logit_ROC <- roc(rough_X2$WAGEX_3, P_Logit$Y)
```

```{r}
Ada_ROC
```



```{r}
par(pty="s")
plot(Ada_ROC,col="blue")
plot(Gbm_ROC,col="green", add=TRUE)
plot(Cart_ROC,col="red", add=TRUE)
plot(Logit_ROC,col="black", add=TRUE)
```

```{r}
Ada_ROC2 <- roc(rough_X2$WAGEX_3, P_Ada$N)
Gbm_ROC2 <- roc(rough_X2$WAGEX_3, P_Gbm$N)
Cart_ROC2 <- roc(rough_X2$WAGEX_3, P_Cart$N)
Logit_ROC2 <- roc(rough_X2$WAGEX_3, P_Logit$N)
```

```{r}
par(pty="s")
plot(Ada_ROC2,col="blue")
plot(Gbm_ROC2,col="green", add=TRUE)
plot(Cart_ROC2,col="red", add=TRUE)
plot(Logit_ROC2,col="black", add=TRUE)
```

```{r}
confusionMatrix(C_Ada,rough_X2$WAGEX_3)
```

```{r}
confusionMatrix(C_Gbm,rough_X2$WAGEX_3)
```

```{r}
confusionMatrix(C_Cart,rough_X2$WAGEX_3)
```

```{r}
prob <- verify(pred = P_Ada$N, obs=ifelse(rough_X2$WAGEX_3 == "N", 1, 0), frcst.type = "prob", obs.type = "binary")
```

```{r}
summary(prob)
```








